Stochastic Variance-Reduced Policy Gradient

### 2018-02-07 svrpg.tex
minor changes to Sec 5.2 and 5.3

\subsection{Normalized Importance Sampling}\label{sec:prac}
As we already mentioned in section \ref{sec:stopping} importance weights means a lot of variance to deal with. Therefore, in order to cope with this issue the literature propose the Self-normalization technique.
This technique offers a variance reduction over the importance weights in exchange of a bias introduction. Hence, if the bias introduced by this is smaller than the variance reduction it causes, it is convenient to use it in practice.  
Introducing self-normalization in the context of our algorithm, we switch from equation \ref{E:svrpg.estimate.batch} to:
\begin{align*}
\blacktriangledown J(\vtheta_{t}) := v_t= \wh{\nabla}_N J(\wt{\vtheta})
 + \frac{1}{B} \sum_{i=0}^{B-1} \left[
g(\tau_i|\vtheta_t)\right]\\ 
- \frac{1}{ \sum_{i=0}^{B-1}\omega(\tau_i|\vtheta_t, \wt{\vtheta})} \sum_{i=0}^{B-1} \left[ \omega(\tau_i|\vtheta_t, \wt{\vtheta}) g(\tau_i|\wt{\vtheta})
\right].
\end{align*}
We experienced some improvements using it (see section \ref{sec:exp} for the experimental point of view).

\subsection{Baseline}
As reported in Sec. \ref{subsec:PolicyGradient} a well known variance reduction tool in Reinforcement Learning is the baseline.
This tool does not depend on SVRPG. More precicely we decided to use an Actor Critic baseline, which is a state dependent linear function with a time-varying feature vector \cite{duan2016benchmarking}. Furthermore, the baseline is unique and computed every snapshot using the N trajectories at hand.

>>>>

\subsection{Normalized Importance Sampling}\label{sec:prac}
As mentioned in section \ref{sec:stopping}, importance weights are an additional source of variance. A common way to cope with this issue is self-normalization.
This technique can reduce the variance of the importance weights at the cost of introducing some bias. Whether the trade-off is advantageous depends on the specific task.  
Introducing self-normalization in the context of our algorithm, we switch from equation \ref{E:svrpg.estimate.batch} to:
\begin{align*}
\blacktriangledown J(\vtheta_{t}) = \wh{\nabla}_N J(\wt{\vtheta})
 + \frac{1}{B} \sum_{i=0}^{B-1} \left[
g(\tau_i|\vtheta_t)\right]\\ 
- \frac{1}{ \sum_{i=0}^{B-1}\omega(\tau_i|\vtheta_t, \wt{\vtheta})} \sum_{i=0}^{B-1} \left[ \omega(\tau_i|\vtheta_t, \wt{\vtheta}) g(\tau_i|\wt{\vtheta})
\right].
\end{align*}
In Section \ref{sec:exp} we show some cases in which self-normalization provides a performance improvement.
\todomat{add reference, maybe just Precup}

\subsection{Baseline}
As reported in Sec. \ref{subsec:PolicyGradient}, a well known variance reduction tool in Reinforcement Learning is the employment of baselines in policy gradient estimation.
This tool is orthogonal to the variance reduction technique proposed in this paper. In Section \ref{sec:exp} we try to combine SVRPG with a non-stationary, state-dependent, learned linear baseline like the one used in \cite{duan2016benchmarking}, with the variant that baseline parameters are updated only at the snapshot, with trajectories sampled from $\pi_{\tilde{\vtheta}^s}$.
